More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-14 2016-Weak-FH-Bisim/WeakBisim.tex
TODO section
improved text of todo
new SV syntax

@@

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,e_k$ where
  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector 
$\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | e_b
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land e_b
\end{array} \bigg)\]

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
    \alpha' |e_b \\
    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\\
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I}\!\! I_m'
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
    \alpha' |e_b \\
    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\\
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I}\!\! I_m'
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip

@@

       Consider each premise of the open transition (constructed by Tr2 in 
Definition~\ref{def:operationalSemantics}). 
We know each premise is true for $P$ and try to prove the equivalent premise for 
$P[Q]_{j_0}$ (using the open transition of $Q$). 
$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
$SV_k=\alpha_j^{j\in I\uplus\{j_0\}\uplus 
	J} \!\to\! 
    \alpha' |e_b$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ are the 
    set of leaves and holes of $P$, $I'$ and $J'$ are the sets of moving leaves and holes 
    in the reduction of $P$. All sub-pNets of 
    must
    be 
reduced:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
%variables}:
\[\forall m\!\!\in\!\! I\cup \{j_0\}. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\]
the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
by hypothesis.
Let $I''=\biguplus_{m\in I} I'_m \uplus I_Q = I' \uplus I_Q$ and $J''= \biguplus_{m\in I} 
J_m \uplus J_Q \uplus J = J'\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
transition is: $\Pred\,''=\bigwedge_{m\in I}\Pred_m \land \Pred\,'
\land \Pred(SV_k,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)$. By definition 
$\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)\Leftrightarrow
	\forall i\in I.\, a_i=\alpha_i\land \forall j \in J.\, b_j=\alpha_j \land 
	\alpha'_k=v\land v_Q=\alpha_{j_0}\land e_b$, finally 
	$\Pred\,''=\Pred\subst{b_{j_0}\leftarrow 
	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 
	the leaves. Finally, the composed open transition can be
        built. \qed
        \end{proof}
\end{small}

>>>>

\section{Status and TODO list}
Improve and simplify Tr2

notation guards in  SV

@@

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
  \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector 
$\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV=\SV{{(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}} {v'} {e_b}
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land e_b
\end{array} \bigg)\]

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I\uplus J}}{\alpha'}{e_b} \\
    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\\
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I}\!\! I_m'
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I\uplus J}}{\alpha'}{e_b} \\
    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\\
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I}\!\! I_m'
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip

@@

       Consider each premise of the open transition (constructed by Tr2 in 
Definition~\ref{def:operationalSemantics}). 
We know each premise is true for $P$ and try to prove the equivalent premise for 
$P[Q]_{j_0}$ (using the open transition of $Q$). 
$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
$SV_k=\SV{\alpha_j^{j\in I\uplus\{j_0\}\uplus 
	J}}{\alpha'}{e_b}$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ 
	are the 
    set of leaves and holes of $P$, $I'$ and $J'$ are the sets of moving leaves and holes 
    in the reduction of $P$. All sub-pNets of 
    must
    be 
reduced:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
%variables}:
\[\forall m\!\!\in\!\! I\cup \{j_0\}. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\]
the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
by hypothesis.
Let $I''=\biguplus_{m\in I} I'_m \uplus I_Q = I' \uplus I_Q$ and $J''= \biguplus_{m\in I} 
J_m \uplus J_Q \uplus J = J'\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
transition is: $\Pred\,''=\bigwedge_{m\in I}\Pred_m \land \Pred\,'
\land \Pred(SV_k,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)$. By definition 
$\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)\Leftrightarrow
	\forall i\in I.\, a_i=\alpha_i\land \forall j \in J.\, b_j=\alpha_j \land 
	\alpha'_k=v\land v_Q=\alpha_{j_0}\land e_b$, finally 
	$\Pred\,''=\Pred\subst{b_{j_0}\leftarrow 
	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 
	the leaves. Finally, the composed open transition can be
        built. \qed
        \end{proof}
\end{small}
